---
title: "Basic_R_Exercise_1_Brianna_Kincaid"
author: "Brianna Kincaid"
date: "January 22, 2018"
output: 
  pdf_document: 
    latex_engine: xelatex
---

## 1. Create the vectors:

###(a) (1; 2; 3; : : : ; 19; 20)
```{r}
1:20
```

###(b) (20; 19; : : : ; 2; 1)
```{r}
20:1
```
###(c) (1; 2; 3; : : : ; 19; 20; 19; 18; : : : ; 2; 1)
```{r}
c(1:20,19:1)
```
###(d) (4; 6; 3) and assign it to the name tmp.
```{r}
tmp <- c(4,6,3)
```
###(e) (4; 6; 3; 4; 6; 3; : : : ; 4; 6; 3) where there are 10 occurrences of 4.
```{r}
rep(tmp, times=10)
```
###(f) (4; 6; 3; 4; 6; 3; : : : ; 4; 6; 3; 4) where there are 11 occurrences of 4, 10 occurrences of 6 and 10 occurrences of 3.
```{r}
rep(tmp, length=31)
```
###(g) (4; 4; : : : ; 4; 6; 6; : : : ; 6; 3; 3; : : : ; 3) where there are 10 occurrences of 4, 20 occurrences of 6 and 30 occurrences of 3.
```{r}
c(rep(4, times=10),rep(6, times=20),rep(3, times=30))
```

##2. Create a vector of the values of e^x cos(x) at x = 3; 3:1; 3:2; : : : ; 6.

```{r}
exp(seq(3,6,.1)) * cos(seq(3,6,.1))
```

##3. Create the following vectors:

### (a) (0:130:21; 0:160:24; : : : ; 0:1360:234)

```{r}

(0.1^(seq(3,36,3)))*(0.2^(seq(1,34,3)))
```

### (b)
```{r}
(2^(1:25))/(1:25)
```
##4. Calculate the following:

###(a)
```{r}
sum(((10:100)^3)+(4*((10:100)^2)))
```
###(b)
```{r}
sum(((2^(1:25))/(1:25)) + ((3^(1:25))/((1:25)^2)))
```

##5. Use the function paste to create the following character vectors of length 30:

###(a) ("label 1", "label 2", ....., "label 30").
###Note that there is a single space between label and the number following.
```{r}
paste("label",(1:30), sep = " ")
```

###(b) ("fn1", "fn2", ..., "fn30").
###In this case, there is no space between fn and the number following.
```{r}
paste("fn",(1:30), sep = "")
```

##6. Execute the following lines which create two vectors of random integers which are chosen with replacement from the integers 0, 1, : : : , 999. Both vectors have length 250.

```{r}
set.seed(50)
xVec <- sample(0:999, 250, replace=T)
yVec <- sample(0:999, 250, replace=T)
```

###Suppose x = (x1; x2; : : : ; xn) denotes the vector xVec and y = (y1; y2; : : : ; yn) denotes the vector yVec.

###(a) Create the vector (y2 􀀀 x1; : : : ; yn 􀀀 xn−1).
```{r}
yVec[-1]-xVec[-length(xVec)]
```

###(b)
```{r}
sin(yVec[-length(yVec)])/cos(xVec[-1])
```

###(c) Create the vector (x1 + 2x2 􀀀 x3; x2 + 2x3 􀀀 x4; : : : ; xn−2 + 2xn−1 􀀀 xn).
```{r}
i <- 1:(length(xVec)-2)
xVec[i] + 2*xVec[i+1] - xVec[i+2]
```
###(d)

```{r}
sum((exp(-xVec[(1:249)+1]))/(xVec[(1:249)]+10))
```

##7. This question uses the vectors xVec and yVec created in the previous question and the functions sort, order, mean, sqrt, sum and abs.

###(a) Pick out the values in yVec which are > 600.
```{r}
yVec[yVec>600]
```
###(b) What are the index positions in yVec of the values which are > 600?
```{r}
which(yVec>600)
```
###(c) What are the values in xVec which correspond to the values in yVec which are > 600? (By correspond, we mean at the same index positions.)
```{r}
xVec[which(yVec>600)]
```
###(d) 
```{r}
sqrt(abs(xVec[(1:250)]-mean(xVec)))
```
###(e) How many values in yVec are within 200 of the maximum value of the terms in yVec?
```{r}
length(yVec[(max(yVec)+200) > yVec & yVec > (max(yVec)-200)])
```
###(f) How many numbers in xVec are divisible by 2? (Note that the modulo operator is denoted %%.)
```{r}
length(xVec[xVec%%2==0])
```
###(g) Sort the numbers in the vector xVec in the order of increasing values in yVec.
```{r}
xVec[(unlist(sort(yVec, index.return = TRUE)[2],use.names=FALSE))]
```
###(h) Pick out the elements in yVec at index positions 1; 4; 7; 10; 13; : : : :
```{r}
yVec[seq(1,length(yVec),3)]
```

##8.By using the function cumprod or otherwise, calculate...

```{r}
num <- c(1,seq(2,38,2))
den <- seq(1,39,2)
x <- num/den

sum(cumprod(x))
```
